Project Light

### 2015-09-09 paper/paper.tex
formulate some paragraphs of related work

- IoT requires own network stack because of special needs: energy and resources, e.g. batteries should work for multiple years and mote memory will be very small (e.g. 48kb program flash for telosB mote CITE SOURCE), many addresses needed
- 6LowPan protocol stack as described in "Standardized protocol stack.." is tailoring this
- its using own implementations of layers, e.g. PHY for physical layer, and CoaP as applicationlayer as well as conventional ones (namely IPv6 as Internet layer) --> enables IoT

- there are some proposals for specialized security layers in this stack, e.g. akes \cite{krentz15akes}
- akes uses session keys and a neighborhood-exploration-technique to gain sufficient security level, even surviving reboots
- it still relies on predistributed keys on each mote
- how to predistribute in safe way?

\cite{chen2011over} proposes key provisioning without wiring using eliptic curve cryptography --> expensive for memory and energy.
- (own chips might solve this, but increase per unit cost)

\cite{kuo2007message} utilizes Faraday cage and another (third) radio jamming device for initialization.
-> requires special hardware

6doku \cite{krentz20156doku} proposes pairing with smartphone and extra-hardware for pairing
- extra hardware and motes need button

@@

Project Light consists of an Android app that creates and sends the keying material and a Contiki\cite{dunkels04contiki} process that runs on the TelosB sky mote and receives and validates it.
Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.

>>>>

In order to make the IoT reality, a specialized network stack is needed.
Motes have special constrains regarding energy and memory resources, e.g. batteries should work for multiple years and a mote's program memory will be very small (e.g. 48kb program flash for telosB mote, \cite{telosb}).
Additionally, typical IoT setups will make use of hundreds of nodes, so there many more addresses needed than the traditional Internet uses.

The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring this needs.
The criteria for IoT network stacks are according to them: low power usage, high reliability, Internet-suitability.
Therefore, tailored implementations of stack layers are presented, like \textit{PHY of IEEE 802.15.4}, which is a power saving physical/link layer.
In order to be Internet-enabled regarding the need for huge amounts of addresses, IPv6 is utilized.
However, in order to save energy, the headers of IPv6 packets are heavily compressed in 6LoWPAN.

There are some proposals for specialized security measures in this stack, e.g. \textit{Adaptive Key Establish- ment Scheme (AKES)}, \cite{krentz15akes}.
AKES makes use of session keys and a neighborhood-exploration-technique to gain sufficient security level while being memory-space-saving.
Security is even obtained after reboots.
It still relies on predistribution keys on each mote.

The problem of wireless and user-friendly key predistribution / key provisioning remains.
There are multiple approaches to solve this:

\begin{itemize}
	\item \cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC). However, while meeting high security standards, software implementations of ECC require a lot of memory space and energy while hardware implementations increase the per-unit cost.
	\item In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a mote can be programmed without interleaving of messages from an attacker outside of the cage. Additionally, a third device outside of the cave jams radio waves to prevent malicious communication.
	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled devices like an smart phone, \cite{krentz20156doku}. The smart phone needs extra hardware attached for communicating with the mote via radio waves. It relies on interaction with the end-user, e.g. he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
\end{itemize}

@@

Project Light consists of an Android app that creates and sends the keying material and a Contiki process that runs on the TelosB sky mote and receives and validates it, \cite{dunkels04contiki}, \cite{telosb}.
Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.
